\LARGE \bf Reactive Trajectory Planning and Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-04-20 root.tex
remove B for body frame

% How we actually did this.
For the purposes of developing a simple example application, two constraints are used for $v_{m}$: legal speed limit $SL$ and lateral acceleration limit $a_{B,y}^{max}$. 
Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation :
\begin{equation}
  v_{m,w}(a_{B,y}) = \sqrt{ | a_{B,y}^{max} / \kappa_{w} | } ~,~ w = 1, ..., W
\end{equation}
where $W$ is the number of waypoints in the sub-path, and $\kappa_{w}$ denotes the path curvature at each point.
For each sub-path point, the value $v_{m,w}(a_{B,y}^{max})$ denotes the speed necessary to obtain the limit lateral acceleration $a^{max}_{B,y}$.

@@

\begin{figure}[tb]
  \centering
  \subfigure[
    The result of dividing a single sub-path into separate segments.
    The clustering algorithm used here sets segments boundaries before and after curves.
    The sub-path segments in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.1 m/s (25 mi/hr).
  ]{
  \label{fig:1Dto2DandSegmentationa}
    \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
  }
  \\
  \subfigure[
    An example of how the sub-path's segment boundaries are determined, as well as how $v_m$ is consolidated to determine the speed ceiling for each segment.
    The x-axis corresponds to distance along the subpath above.
    The legal speed limit of 11.1 m/s (25 mi/hr) is shown in cyan.
    The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
    The resultant speed ceiling ($v_m$) is shown in blue.
  ]{
  \label{fig:1Dto2DandSegmentationb}
  \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling.png}
  }
  \caption{Dividing a subpath into segments and determining speed ceilings for each segment.}
  \label{fig:1Dto2DandSegmentation}
\end{figure}

In the consolidation step, a single set of $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ 
must be calculated for each segment using the values corresponding to the waypoints comprising the segment.
The principle task is to find a value of $v_m$ for each segment using the values from segmentation, $SL$ and $v_{m,w}(a_{B,y}^{max})$. 
The value of the speed ceiling for segment $k$ is chosen to be:
\begin{equation}
  v_{m,k} = min \left ( \mathbf{SL}_k ,  \mathbf{v}_{m}(a_{B,y}^{max}) |_k \right )
\end{equation}
where $\mathbf{SL}_k$ is the vector containing the values of the legal speed limit at every way-point in segment $k$.
The vector $\mathbf{v}_{m}(a_{B,y}^{max}) |_k$ contains the values of the speed limit from lateral acceleration at every way-point in segment $k$.
% The minimum of scalar across all constituent points is chosen.
While not time optimal, choosing the minimum of these values over the entire segment ensures that no constraints are violated. As a result, many of the curves have a constant speed.
For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are initially all set constant for the entire path, using values from \cite{Maurya2012,Hoberock1977,Long2000}.
Once the values $v_{m,k}$ are set for every segment in the subpath, boundary conditions must be set to ensure that speed is continuous between segments. Acceleration continuity will be addressed later.
The algorithm in Fig. \ref{alg:segmentspeedboundaryconditions} is used to compute the vector $\mathbf{v}_p$ and then each segment $k$ can be solved using:
\begin{equation}
  v_{i,k} = v_{f,k-1} = v_{p,k}
\end{equation}

@@

% After stitching together control point vectors for time, position, and its derivatives, all information required to have a trajectory plan is now in place.
% To aid in this, univariate splines are created with time as the independent variable, using the control points as knots.
% Position along the path as a function of reference plan time, $s(t)$, takes the form of a cubic Hermite spline, constructed using the speed control points $v_{B,x}(t)$ to set the derivatives.
% Speed along the path $v_{B,x}(t)$ takes the form of a quadratic Hermite spline, with the acceleration control points $a_{B,x}(t)$ used to set the derivatives at every knot.
% Acceleration $a_{B,x}(t)$ is piecewise linear, so lookup is a trivial matter.
% The same applies to $j_{B,x}(t)$, which may be implemented with a simple table.

@@

Now the reference time corresponding to the vehicle's location $t_{veh}$ is needed to look up $v_{B,x}(t_{veh})$, $a_{B,x}(t_{veh})$, and $j_{B,x}(t_{veh})$.
Additionally, it is also needed to sample $s(t)$ at intervals ahead of the vehicle.
Since it is known that $s(t)$ is piecewise cubic, reference time as a function of vehicle position along the path, $t(s)$, may be approximated as cubic using a spline.
To get the knots, $s(t)$ is sampled at $\Delta t = 0.01 sec$.
This yields two vectors $s'$ and $t'$ which are then used to create a univariate cubic $t(s)$ spline.
Evaluating $t(s_{veh})$ then yields the current reference time.

>>>>

% How we actually did this.
For the purposes of developing a simple example application, two constraints are used for $v_{m}$: legal speed limit $SL$ and lateral acceleration limit $a_{y}^{max}$. 
Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation :
\begin{equation}
  v_{m,w}(a_{y}) = \sqrt{ | a_{y}^{max} / \kappa_{w} | } ~,~ w = 1, ..., W
\end{equation}
where $W$ is the number of waypoints in the sub-path, and $\kappa_{w}$ denotes the path curvature at each point.
For each sub-path point, the value $v_{m,w}(a_{y}^{max})$ denotes the speed necessary to obtain the limit lateral acceleration $a^{max}_{y}$.

@@

\begin{figure}[tb]
  \centering
  \subfigure[
    The result of dividing a single sub-path into separate segments.
    The clustering algorithm used here sets segments boundaries before and after curves.
    The sub-path segments in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.1 m/s (25 mi/hr).
  ]{
  \label{fig:1Dto2DandSegmentationa}
    \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
  }
  \\
  \subfigure[
    An example of how the sub-path's segment boundaries are determined, as well as how $v_m$ is consolidated to determine the speed ceiling for each segment.
    The x-axis corresponds to distance along the subpath above.
    The legal speed limit of 11.1 m/s (25 mi/hr) is shown in cyan.
    The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
    The resultant speed ceiling ($v_m$) is shown in blue.
  ]{
  \label{fig:1Dto2DandSegmentationb}
  \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling2.PNG}
  }
  \caption{Dividing a subpath into segments and determining speed ceilings for each segment.}
  \label{fig:1Dto2DandSegmentation}
\end{figure}

In the consolidation step, a single set of $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ 
must be calculated for each segment using the values corresponding to the waypoints comprising the segment.
The principle task is to find a value of $v_m$ for each segment using the values from segmentation, $SL$ and $v_{m,w}(a_{y}^{max})$. 
The value of the speed ceiling for segment $k$ is chosen to be:
\begin{equation}
  v_{m,k} = min \left ( \mathbf{SL}_k ,  \mathbf{v}_{m}(a_{y}^{max}) |_k \right )
\end{equation}
where $\mathbf{SL}_k$ is the vector containing the values of the legal speed limit at every way-point in segment $k$.
The vector $\mathbf{v}_{m}(a_{y}^{max}) |_k$ contains the values of the speed limit from lateral acceleration at every way-point in segment $k$.
% The minimum of scalar across all constituent points is chosen.
While not time optimal, choosing the minimum of these values over the entire segment ensures that no constraints are violated. As a result, many of the curves have a constant speed.
For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are initially all set constant for the entire path, using values from \cite{Maurya2012,Hoberock1977,Long2000}.
Once the values $v_{m,k}$ are set for every segment in the subpath, boundary conditions must be set to ensure that speed is continuous between segments. Acceleration continuity will be addressed later.
The algorithm in Fig. \ref{alg:segmentspeedboundaryconditions} is used to compute the vector $\mathbf{v}_p$ and then each segment $k$ can be solved using:
\begin{equation}
  v_{i,k} = v_{f,k-1} = v_{p,k}
\end{equation}

@@

% After stitching together control point vectors for time, position, and its derivatives, all information required to have a trajectory plan is now in place.
% To aid in this, univariate splines are created with time as the independent variable, using the control points as knots.
% Position along the path as a function of reference plan time, $s(t)$, takes the form of a cubic Hermite spline, constructed using the speed control points $v_{x}(t)$ to set the derivatives.
% Speed along the path $v_{x}(t)$ takes the form of a quadratic Hermite spline, with the acceleration control points $a_{x}(t)$ used to set the derivatives at every knot.
% Acceleration $a_{x}(t)$ is piecewise linear, so lookup is a trivial matter.
% The same applies to $j_{x}(t)$, which may be implemented with a simple table.

@@

Now the reference time corresponding to the vehicle's location $t_{veh}$ is needed to look up $v_{x}(t_{veh})$, $a_{x}(t_{veh})$, and $j_{x}(t_{veh})$.
Additionally, it is also needed to sample $s(t)$ at intervals ahead of the vehicle.
Since it is known that $s(t)$ is piecewise cubic, reference time as a function of vehicle position along the path, $t(s)$, may be approximated as cubic using a spline.
To get the knots, $s(t)$ is sampled at $\Delta t = 0.01 sec$.
This yields two vectors $s'$ and $t'$ which are then used to create a univariate cubic $t(s)$ spline.
Evaluating $t(s_{veh})$ then yields the current reference time.
